Designing an effective intervention of motivational interview using sequence classification methods

### 2017-02-28 paper/AMIA/main.tex
update conclusion

\section*{Conclusion}
It has been shown how Hidden Markov Models could be used to build classifiers for the sequence of behavior codes in motivational interviews. In this work, we suggest some successful sequences of codes for the practical use by the clinician during the interview session which will translate into positive change talk and commitment language. This work can facilitate researchers to establish causal relationship between different communication strategies and desired behavioral outcomes without having to repeatedly wade through pages of interview transcripts. Information that can directly inform and increase the efficiency of clinical practice for a successful interview. Direction of future work include the exploration of other methods such as BLAST \cite{altschul1990basic} and Strand \cite{drew2014strand} for the classification of utterance sequences.

>>>>

\section*{Conclusion}
It has been shown how Markov chain and Hidden Markov Models could be used to build classifiers for the sequence of behavior codes in motivational interviews. Experimental results shows that the behavior codes carry some inherited information to distinguish motivational interviews. This work can facilitate researchers to establish causal relationship between different communication strategies and desired behavioral outcomes without having to repeatedly wade through pages of interview transcripts. It provides information that can directly inform and increase the efficiency of clinical practice for a successful interview. This work also suggest some successful patterns for the practical use by the clinician during the interview session which will translate into positive change talk and commitment language. Direction of future work include the exploration of other methods such as BLAST \cite{altschul1990basic} and Strand \cite{drew2014strand} for the classification of utterance sequences. We also have plan to use large data set in conjunction with some advanced features for the evaluation of sequence classifiers.
